### 2021-03-10 results/draft.tex
small changes
tidy up

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology.
Field surveys using environmental DNA (eDNA) are widely used for detecting invesive or rare species and hotspot of biodiversity (面倒なのでレビュー論文を引用) because the surveys of eDNA are easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al. 2014; Thomsen \& Willerslev 2015 #Dorazioに引用されていたやつ．あとで再確認).
%Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
However, the presence/absence of eDNA includes many types of uncertinties due to relating to environmental factors such as temperature and advection ().
For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.
Therefore, the consideration to the influence of environmental factors on eDNA is necessary for estimation of species distribution when we use eDNA methods.

@@

\ \ \ \ \ \ \ \ \ \
Integrated species distribution models are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data wihch is widely collected and abundant, and combine in a single model (Isaac et al. 2020; Miller et al. 2019).

@@

\ \ \ \ \ \ \ \ \ \
Tokyo Bay is a large enclosed coastal sea in Japan. In Tokyo Bay, there are many useful species for fisheries that are colled "Edomae" because these species have been used for Sushi since Edo Era (about 400 years ago). Catch of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution). Catch statistics (total catch in each fish, efforts, and geographic location of fishing) have been collected for stock assessment since 1990 by prefectures around Tokyo Bay, which is widely collected and abundant.
In addition, scientific survey of eDNA has been conducted monthly in same points since 2018 for monitoring biodiveristy (Hongo et al., submitted).

\ \ \ \ \ \ \ \ \ \
In this paper, we demonstrate a method for reducing identification error by using the state-of-the-art spatio--temporal standardization method (Thorson 2019). Our {new application substantially reduced the bias that would have been caused by the species misidentification of spawning eggs between chub mackerel and spotted mackerel and led to considerable improvement in the stock assessment of spotted mackerel in the western North Pacific. To quantify the effect of species misidentification, we estimated the indices of egg density for spotted mackerel both with and without incorporation of the effect of the egg density of chub mackerel on the catchability of spotted mackerel, using 15 years data of spawning eggs. We then examined how retrospective biases of three measurements of stock abundance (total number of individuals, total stock biomass, and spawning stock biomass; SSB) changed when we used the estimated indices for a stock assessment model. We tested the hypothesis that the retrospective bias should be lower in the spotted mackerel stock assessment with the egg--abundance index standardized by the spatio--temporal model incorporating chub mackerel egg density as a catchability covariate.

@@

\ \ \ \ \ \ \ \ \ \
The probability density function of $\omega(\cdot)$ is a multivariate normal distribution $\mathrm{MVN}(0, \mathbf{R})$, where the variance--covariance matrix $\mathbf{R}$ is a Mat\'{e}rn correlation function. The probability density function of $\varepsilon(s_{i}, t_{i})$ is
\[\
\varepsilon(\cdot, t_{i}) \sim \left\{
\begin{array}{ll}
\mathrm{MVN}(0, \mathbf{R}), &if \;t = 1\\
\mathrm{MVN}(\rho_{\varepsilon} \varepsilon(\cdot, t-1_{i}), \mathbf{R}), &if \;t > 1 \\
\end{array} \right.
. \]
Here, we set $\rho_{\varepsilon} = 0$ under the assumption that the year was independent. Therefore, the probability density function of $\eta(v_{i})$ is $\eta(v_{i}) \sim \mathrm{N}(0, 1)$.

\ \ \ \ \ \ \ \ \ \
For computational reasons, the spatio-temporal variation $\varepsilon_{p}(s_{i}, t_{i})$ was approximated as being piecewise constant at a fine spatial scale. We used a k-means algorithm to identify 200 locations (termed ``knots'') to minimize the total distance between the location of sampling data (Thorson et al., 2015) using R-INLA software (Lindgren, 2012). The number of knots was increased to the greatest extent possible, and similar results were obtained for low knots (= 100; Akaike information criterion [AIC] = 6773.01) and high knots (= 200; AIC = 6676.25).

\ \ \ \ \ \ \ \ \ \
Parameters in the VAST model were estimated using the VAST package (Thorson et al., 2015,2016a) in R 3.6.1 (R Development Core Team, 2019). Bias-correction for random effects (Thorson and Kristensen, 2016) was applied when estimating the derived parameters. We evaluated the model diagnostics plots and confirmed that there were no serious problems with the model. The relative egg density in year $t$ at location $s$, $\hat{d}(s, t)$ and the index of egg density in year $t$, $\hat{D}(t)$, were estimated using the predicted values for random effects as follows (Thorson et al., 2017):
\newpage
\[
\hat{d}(s, t) = \mathrm{logit}^{-1}[\beta_{p}(t_{i}) + \omega_{p}(s_{i}) + \varepsilon_{p}(s_{i}, t_{i}) + \eta_{p}(v_{i})]
\]
\[
\times \exp[\beta_{d}(t_{i}) + \omega_{d}(s_{i}) + \varepsilon_{d}(s_{i}, t_{i}) + \eta_{d}(v_{i})],
\]
\[\hat{D}(t) = \sum_{s} a(s) \times \hat{d}(s, t)
\]

%\[
%\begin{split}
%\hat{d}(s, t) = \mathrm{logit}^{-1}[\beta_{p}(t_{i}) + \omega_{p}(s_{i}) + \varepsilon_{p}(s_{i}, t_{i}) + \eta_{p}(v_{i}) + \lambda_{p}Q(i)]\\
 %\times \exp[\beta_{d}(t_{i}) + \omega_{d}(s_{i}) + \varepsilon_{d}(s_{i}, t_{i}) + \eta_{d}(v_{i}) + \lambda_{d}Q(i)],
% \end{split}
%\]
%\[\hat{D}(t) = \sum_{s} a(s) \times \hat{d}(s, t)
%\]
where $a (s)$ is the area of location $s$. It is noteworthy that  the effect of the catchability covariate $\lambda Q(i)$ in the above equation (1) is removed in the calculation of densities. This means that the abundance index can be derived from the model by removing the bias from the contamination of spotted mackerel eggs with chub mackerel eggs.

\flushleft{\textbf{2.2.3 Estimation of stock abundance}}\\
To examine the validity of the three indices (i.e., nominal index, chub- index, and chub+ index), we estimated the three measurements of stock abundance (total number of individuals, total stock biomass, and SSB) from 1995 to 2018 using a tuned virtual population analysis (VPA). This model is an age-based cohort analysis for estimating the historical abundance and fishing mortality rates from catch-at-age data and has been applied to spotted mackerel in Japan (Yukami et al., 2019). In addition to the three indices of egg density, we used catch-at-age, weight-at-age (not constant over time), maturity-at-age (constant over time) for four age categories (1 to 3, and 4+), the natural mortality coefficient, and a recruitment index following stock assessment in Japan (Yukami et al., 2019). The fishing mortality coefficients other than the terminal age in the terminal year were estimated under the assumption that the selectivity in the latest year was equal to the average selectivity of the prior 5 years (Ichinokawa and Okamura, 2014; Mori and Hiyama, 2014). We confirmed that this assumption did not change our results when using the average selectivity of the prior 3 years as the selectivity in the latest year. The fishing mortality coefficient at each age in the terminal year was estimated by a maximum likelihood method as follows:
\[\sum_{k} \sum_{y} \left[ \frac{\{\mathrm{log}(I_{k,y})-\mathrm{log}(q_{k}X_{k,y})\}^2} {2\sigma^{2}} - \mathrm{log}(\frac{1} {\sqrt{2\pi\sigma^{2}}}) \right]
,\]
where $I_{k,y}$ is the value of index $k$ in year $y$, $q_{k}$ is a proportionality constant, $X_{k,y}$ is the abundance estimate in VPA for index $k$ (i.e., recruitment, and the three indices of egg density), $\sigma^2$ is the variance in fitting the abundance estimate to the index, and $y_{k}$ is the first year of index $k$.

\flushleft{\textbf{2.2.4 Retrospective analysis}}\\
Stock abundance in the terminal year estimated by VPA is notoriously inaccurate and imprecise compared with historical abundance estimates (Okamura et al. 2017). One of the most serious problems is that the stock abundance estimate in the terminal year has temporally systematic bias, i.e., retrospective bias (Hurtado-Ferro et al. 2015). Retrospective analysis is therefore a useful method for detecting such a systematic bias in stock abundance estimate in the terminal year. Dropping the most recent year's data sequentially and then comparing the estimates from a full-year data model and removed data model reveals presence or absence of systematic bias (Mohn 1999). Herein, we conduct a retrospective analysis to evaluate the relative goodness of estimation of stock abundance for} three indices of egg density.

\ \ \ \ \ \ \ \ \ \
To examine improvements in estimations of the three measurements of stock abundance when using the estimated indices of egg density from the VAST model and considering the effect of the chub mackerel, we performed a retrospective analysis by sequentially removing the five most recent years of data from the full data set. Retrospective analysis is usually used in stock assessment models such as VPA to examine the reliability and predictability of stock assessments (e.g., Mohn, 1999; Hashimoto et al., 2018). We calculated Mohn's rho to estimate the biases of the indices of egg density as follows (Mohn, 1999):
\[\rho = \frac{1}{c} \sum_{i}^{c} \left(\frac{B_{y-i}^R - B_{y-i}} {B_{y-i}} \right)
,\]
where $B_{y-i}$ is the value of the year $y-i$ estimate using the full data and $B_{y-i}^R$ is the estimate using the data up to year $y-i$. $c$ is the maximum number of removed years (i.e., $c = 5$). A positive $\rho$ means that the estimate in the terminal year tends to be positively biased on average, and vice versa. Moreover, a $\rho$ close to $0$ means no serious retrospective bias and greatly improved estimation of the stock abundance.

\ \\
\section{Results}
\flushleft{\textbf{3.1 Temporal trend in the indices of egg density}}\\
When comparing the standardized indices (i.e., chub- and chub+ indices) to the nominal index, the standardized indices reduced temporal fluctuation (Fig. 2). Whereas the nominal index increased substantially in 2018, the standardized indices were reduced to a considerable degree. Moreover, the standardized indices for some years, such as 2008, 2009, and 2012, were increased.

\ \ \ \ \ \ \ \ \ \
The model with the effect of chub mackerel egg density on the catchability of spotted mackerel was more parsimonius than the model without the effect of chub mackerel based on AIC (chub+, AIC = 8250.12; chub--, AIC = 8978.81). The coefficient of the effect of chub mackerel on the catchability of spotted mackerel, $\lambda$, indicates a positive effect ($\lambda$ = 0.17). The estimated index with the effect of chub mackerel effect reached a peak in 2008 and decreased gradually thereafter. The value of this index in 2019 was the lowest since 2005 (Fig. 2).

\flushleft{\textbf{3.2 Spatial distribution of the relative egg density}}\\
The relative egg density with the effect of chub mackerel was high off the coast of Kyushu, Shikoku, and the Izu Islands (Fig. 3). In addition, the relative egg density was slightly high off the coast of the Tohoku region. These patterns were consistent during the study period. The relative egg density did not clearly increase or decrease in any area during the study period.

\flushleft{\textbf{3.3 Retrospective analysis}}\\
Recent estimated values of stock abundance (i.e., total numbers of individuals, total biomass, and SSB) differed depending on the indices used, whereas the directions of retrospective bias were sometimes consistent depending on the indices used (Fig. 4). In all the three measurements of stock abundance, the recent estimated values were higher when using the nominal and estimated index without the effect of chub mackerel than using the estimated index with the effect of chub mackerel. The directions of retrospective bias were always positive, independent of the indices used.

\ \ \ \ \ \ \ \ \ \
For all the three measurements of stock abundance (i.e., total numbers of individuals, total biomass, and SSB), retrospective biases clearly improved when using the estimated index with the effect of chub mackerel (Table 1). Values of Mohn's rho, which represents the magnitude and direction of retrospective bias, were similar when using the nominal index and the estimated index without the effect of chub mackerel (Table 1). In contrast, Mohn's rho decreased when using the estimated index with the effect of chub mackerel. The directions of the retrospective bias did not change depending on the indices used because the values of Mohn's rho were always positive.

\ \\
\section{Discussion}
We modelled the species identification error by linking the catchability of spotted mackerel eggs to the egg density of chub mackerel. We found that the model incorporating the effect of the egg density of chub mackerel was better, based on AIC (Fig. 2). In addition, the model showed that the egg density of chub mackerel had a positive effect on the catchability of spotted mackerel. These results suggest the necessity of incorporating the effect of the egg density of chub mackerel when standardizing the egg density of spotted mackerel.

\ \ \ \ \ \ \ \ \ \
Whereas the nominal index increased substantially in 2018, the standardized indices of chub- and chub+ were similarly reduced (Fig. 2). The reduction in both standardized indices, irrespective of whether the effect of the egg density of chub mackerel was incorporated, may be explained by spatio--temporal changes in survey design, survey effort, and observation rate by the VAST model. Indeed, the surveys in 2018 were conducted. by chance, at the site with a high egg density of spotted mackerel (Yukami et al., 2019), which was spatially smoothed by considering the spatial correlation using the VAST model. Hence, we think that the nominal index in 2018 included both species identification bias and spatio--temporal bias from the survey.

\ \ \ \ \ \ \ \ \ \
The retrospective biases in all the three measurements of stock abundance were clearly improved when using the estimated index that incorporates the effect of chub mackerel; the magnitude of the retrospective biases decreased by about half compared with those for the other indices (Fig. 4 and Table 1). These results suggest that our new application is effective for reducing the bias in species misidentification and greatly improves stock estimation, especially for pelagic eggs, which have relatively minor differences in shape and size for species identification.
\textcolor{red}{The samples are usually fixed with formalin to preserve their morphological characteristics, which makes DNA extraction difficult or impossible due to DNA fragmentation and protein cross-linking (e.g., Goelz et al., 1985; Impraim et al., 1987).} Accordingly, samples collected prior to the development of DNA techniques cannot used for DNA analysis. In contrast, our new method requires only the geographic locations and ``prior-" information, such as the species name (which can be based on morphological characteristics), to use various data types, such as survey data for eggs and larvae collected in the ICES area. Thus, our method should be of great benefit in fisheries science.

\ \ \ \ \ \ \ \ \ \
Our results can play an important role in the actual management of spotted mackerel. The stock status and management of this species have received substantial attention in Japan because this species is one of the nine TAC (total allowable catch) species, whose catches are strictly managed according to output control. In fact, a new harvest control rule based on maximum sustainable yield (MSY) was implemented in 2020 (Yukami et al. 2020). The stock abundance of spotted mackerel has been decreasing in recent years, and positive retrospective bias caused overestimates of abundance in the terminal year in a previous stock assessment using an unstandardized index of spawning eggs (Yukami et al. 2019). This indicates that the allowable biological catch (ABC) was also overestimated, and this may have led to overfishing.
The stock assessments with the nominal and chub- indices would estimate, respectively, 140 and 105 thousand tons as ABC in 2020, whilst that with the chub+ index would derive 38 thousand tons as ABC in 2020. The present study found that the retrospective bias was considerably reduced in the stock assessment with the chub+ index and this approach would therefore contribute to the derivation of an adequate ABC. Although the current status is overfishing and overfished (Yukami et al. 2020), it is expected that the Pacific stock of spotted mackerel will show a recovery to a level that produces the MSY by using our assessment method and the new Harvest Control Rules.

\ \ \ \ \ \ \ \ \ \
Although detailed information on spawning grounds is necessary for understanding fluctuations in recruitment as well as for providing a basis for stock management, prior data for spotted mackerel has not been reliable. For example, some studies have reported that the area around the Izu Islands may not be a suitable spawning ground for spotted mackerel because few eggs have been observed (Yukami et al. 2019). In contrast, it is possible that the spotted mackerel spawns around the Izu Islands because the estimated hatch day and the spatial distribution of spotted mackerel at the Kuroshio--Oyashio transition area were similar to those of chub mackerel, which spawns around mainly the Izu Islands (Takahashi et al., 2010). The present study showed that the relative egg density, which was estimated using the better model, was equally high off the coast of Kyushu, Shikoku, and the Izu Islands (Fig. 3), providing direct evidence that the area around the Izu Islands are also a major spawning ground of spotted mackerel. It is possible that spotted mackerel spawn in the area around the Izu Islands because they are not sensitive to rising water temperatures and they are generally distributed farther south than chub mackerel (Mitani et al., 2002). Indeed, although both spotted mackerel and chub mackerel spawn at the same time around the Izu Islands (Tanoue et al., 1960; Hanai and Meguro, 1997), the reproductive phenology of chub mackerel has changed due to rising sea surface temperatures associated with climate change; since 2000, chub mackerel migrate to their feeding ground earlier and spawn father northward (Kanamori et al., 2019).

\ \ \ \ \ \ \ \ \ \
Understanding migration patterns is necessary for conducting stock assessments (Crossin et al., 2017). It has been assumed that the spawning grounds of spotted mackerel change with age; individuals migrate from around the Izu Islands to the Kuroshio--Oyashio transition area to feed before spawning at 2 years of age (Nishida et al., 2000; Kawabata et al. 2008). Adults that have spawned gradually migrate westward, using the spawning grounds off the coast of Kyushu and Shikoku (Hanai, 1999; Nashida et al., 2006). Although the number of recruits were particularly high in 2004 and 2009 (Yukami et al., 2019), we did not find evidence for an increase in the relative egg density around the Izu Islands in 2006 and in 2011 or the other spawning grounds after 2007 and 2012 (Fig. 3). One explanation for this is that the migration range of spotted mackerel is narrower than we assumed. Previous studies have reported that spotted mackerel remains around the Izu Islands and off the coast of Shikoku (Hanai, 1999; Nashida et al., 2006). Another explanation is that part of a strong year may remain in another area due to the expansion of the spatial distribution resulting from an increase number in recruitments. For example, Kawabata et al. (2008) reported that the 2004 year class migrated for feeding and overwintering until at least 3 years old over the Emperor Seamounts (around $\textrm{165}-\textrm{170}^{\circ}$E and $\textrm{30}-\textrm{55}^{\circ}$N). Testing these hypotheses will be the subject of future research and should improve our understanding of the migratory patterns of the spotted mackerel, which in turn should improve stock assessment and management.
\ \\

\ \\
\flushleft{\textbf{\Large{Conclusion}}}\\
This study showed that indices of egg density of spotted mackerel, which were standardized using a spatio--temporal model, reduced temporal fluctuation. In particular, the standardized indices in 2018 were reduced to a considerable degree compared with the nominal index. The model incorporating the effect of chub mackerel egg density on the catchability of spotted mackerel (i.e., the model incorporating species misidentification bias) was the better model according to the AIC. In addition, the retrospective bias decreased by about half when using the egg density index from the better model. These results suggest that incorporating species misidentification bias is an essential process for improving stock assessment.

\ \\
%\setstretch{1}
\flushleft{\textbf{\Large{Acknowledgments}}}\\
This research was financiallysupportted by the grants from the Japan Society for the Promotion of Science (JSPS) (19K15905, 20392904).
\ \\

%\flushleft{\textbf{\Large{Authorship}}}\\
%YK conceived of the research idea. AT and MW conducted field sampling. YK, SN, and HO designed statistical analyses. YK and SN wrote programs and performed the analyses. YK wrote the manuscript with input from all co-authors' comments.
\ \\

%\setstretch{1}
\flushleft{\textbf{\Large{Literature cited}}}\\
\hangindent=30pt
\noindent
Crossin, G.T., Cooke, S.J., Goldbogen, J.A., Phillips, R.A. 2014. Tracking fitness in marine vertebrates: current knowledge and opportunities for future research. Mar. Ecol. Prog. Ser. 496:1-17.

\hangindent=30pt
\noindent
Elphick, C.S. 2008. How you count counts: the importance of methods research in applied ecology. J. Appl. Ecol. 45:1313-1320.

\hangindent=30pt
\noindent
Garcia-Vazquez, E., Machado-Schiaffino, G., Campo ,D., Juanes, F. 2012. Species misidentification in mixed hake fisheries may lead to overexploitation and population bottlenecks. Fish. Res. 114:52-55.

\hangindent=30pt
\noindent
Goelz, S.E., Hamilton, S.R., Vogelstein, B. 1985. Purification of DNA from formaldehyde fixed and paraffin embedded human tissue. Biochem. Biophys. Res. Commun. 130:118–126.

\hangindent=30pt
\noindent
Hashimoto, M., Nishijima, S., Yukami, R., Watanabe, C., Kamimura, Y., Furuichi, S., Ichinokawa, M., Okamura, H. 2019. Spatiotemporal dynamics of the Pacific chub mackerel revealed by standardized abundance indices. Fish. Res. 219:105315.

\hangindent=30pt
\noindent
Hashimoto, M., Okamura, H., Ichinokawa, M., Hiramatsu, K., Yamakawa, T. 2018. Impacts of the nonlinear relationship between abundance and its index in a tuned virtual population analysis. Fish. Sci. 84:335-347.

\hangindent=30pt
\noindent
Hurtado-Ferro, F., Szuwalski, C.S., Valero. J.L., Andderson. S.C., Cunningham, C.J., Johnson, K.F., Licandeo, R.L., McGilliard, C.R., Monnahan, C.C., Muradian, M.L., Ono, K., Vert-Pre, K.A., Whitten, A.R., Punt, A.E. 2015. Looking in the review mirror: bias and retrospective patterns in integrated, age-structured stock assessment models. ICES J. Mar. Sci. 72:99-110.

\hangindent=30pt
\noindent
Ichinokawa, M., Okamura, H. 2014. Review of stock evaluation methods using VPA for fishery stocks in Japan: implementation with R. Bull. Jpn. Soc. Fish. Oceanogr. 78:104-113 (in Japanese with English abstract).

\hangindent=30pt
\noindent
Impraim, C.C., Saiki. R.K., Erlich, H.A., Teplitz, R.L. 1987. Analysis of DNA extracted from formalin-fixed, paraffin-embedded tissues by enzymatic amplification and hybridization with sequence-specific oligonucleotides. Biochem. Biophys. Res. Commun. 142:710–716.

\hangindent=30pt
\noindent
Kanamori, Y., Takasuka, A., Nishijima, S., Okamura, H. 2019. Climate change shifts the spawning ground northward and extends the spawning period of chub mackerel in the western North Pacific. Mar. Ecol. Prog. Ser. 624:155-166.

\hangindent=30pt
\noindent
Ko, H.L., Wang, Y.T., Chiu, T.S., Lee, M.A., Leu, M.Y., Chang, K.Z. et al. 2013. Evaluating the accuracy of morphological identification of larval fishes by applying DNA barcoding. PLoS ONE 8:e53451.

\hangindent=30pt
\noindent
Lindgren, F. 2012. Continuous domain spatial models in R-INLA. ISBA Bull. 19:14-20.

\hangindent=30pt
\noindent
MacKenzie, D.I., Nichols, J.D., Lanchman, G.B., Droege, S., Royle, J.A., Langtimm, C.A. 2002. Estimating site occupancy rates when detection probabilities are less than one. Ecology 83:2248-2255.

\hangindent=30pt
\noindent
Marko, P.B., Lee, S.C., Rice, A.M., Gramling, J.M., Fitzhenry, T.M., McAlister, J.S., Harper, G.R., Moran, A.L. 2004. Mislabelling of a depleted reef fish. Nature 430:309-310.

\hangindent=30pt
\noindent
Matarese, A.C., Spies, I.B., Busby, M.S., Orr, J.W. 2011. Early larvae of \textit{Zesticelus profundorum} (family Cottidae) identified using DNA barcording. Ichthyol. Res. 58: 170-174.

\hangindent=30pt
\noindent
Mohn, R. 1999. The retrospective problem in sequential population analysis: an investigation using cod fishery and simulated data. ICES J. Mar. Sci. 56:473-488.

\hangindent=30pt
\noindent
Mori, K., Hiyama, Y. 2014. Stock assessment and management for walleye pollock in Japan. Fish. Sci. 80:161-172.

\hangindent=30pt
\noindent
Nishida, H., Wada, T., Oozeki, Y., Sezaki, K., Saito, M. 2001. Possibility of identifying chub mackerel and spotted mackerel by measuring diameter of mackerel eggs. Nippon Suisan Gakkaishi, 67: 102-104.

\hangindent=30pt
\noindent
Okamura, H., Yamashita, Y., Ichinokawa, M. 2017. Ridge virtual population analysis to reduce the instability of fishing mortalities in the terminal year. ICES J. Mar. Sci. 74:2427-2436.

\hangindent=30pt
\noindent
R Development Core Team, 2019. R: a language and envi- ronment for statistical computing. R Foundation for Sta- tistical Computing, Vienna.

\hangindent=30pt
\noindent
Takahashi, M., Takagi, K,, Kawabata, A., Watanabe, C., Nishida, H., Yamashita, N., Mori, K., Suyama, S., Nakagami, M., Ueno, Y., Saito, M. 2010. Estimated hatching season of the Pacific stock of chub mackerel \textit{Scomber japonicus} and spotted mackerel \textit{S. australasicus} in 2007. Fisheries biology and oceanography in the Kuroshio 11:49-54 (in Japanese).

\hangindent=30pt
\noindent
Takasuka, A., Kubota, Hm., Oozeki, Y. 2008a. Spawning overlap of anchovy and sardine in the western North Pacific. Mar. Ecol. Prog. Ser. 366:231-244.

\hangindent=30pt
\noindent
Takasuka, A., Oozeki, Y., Kubota, H. 2008b. Multi-species regime shifts reflected in spawning temperature optima of small pelagic fish in the western North Pacific. Mar. Ecol. Prog. Ser. 360:211-217.

\hangindent=30pt
\noindent
Takasuka, A., Tadokoro, K., Okazaki, Y., Ichikawa, T., Sugisaki, H., Kuroda, H., Oozeki, Y. 2017. In situ filtering rate vari- ability in egg and larval surveys off the Pacific coast of Japan: Do plankton nets clog or over-filter in the sea? Deep-Sea Res. I 120:132−137.

\hangindent=30pt
\noindent
Takasuka, A., Yoneda, M., Oozeki, Y. 2019. Density depend- ence in total egg production per spawner for marine fish. Fish. Fish. 20:125−137.

\hangindent=30pt
\noindent
Thorson, J.T. 2019.  Guidance for decisions using the Vector Autoregressive Spatio-Temporal (VAST) package in stock, ecosystem, habitat and climate assessments. Fish. Res. 210:143-161.

\hangindent=30pt
\noindent
Thorson, J.T., Barnett, L.A.K. 2017. Comparing estimates of abundance trends and distribution shifts using single- and multispecies models of fishes and biogenic habitat. ICES J. Mar. Sci. 74:1311−1321.

\hangindent=30pt
\noindent
Thorson, J.T., Kristensen, K. 2016. Implementing a generic method for bias correction in statistical models using ran- dom effects, with spatial and population dynamics exam- ples. Fish. Res. 175: 66–74.

\hangindent=30pt
\noindent
Thorson, J.T., Shelton, A.O., Ward, E.J., Skaug, H.J. 2015. Geostatistical delta-generalized linear mixed models improve precision for estimated abundance indices for West Coast groundfishes. ICES J. Mar. Sci. 72:1297−1310.

\hangindent=30pt
\noindent
Victor, B.C., Hanner, R., Shivji, M., Hyde, J., Caldow, C. 2009. Identification of the larval and juvenile stages of the cubera snapper, \textit{Lutignus cyanopterus}, using DNA barcoding. Zootaxa 2215:24-36.

\hangindent=30pt
\noindent
Watanabe, C., Hanai, T., Meguro, K., Ogino, R., Kubota, Y., Kimura, R. 1999. Spawning biomass estimates of chub mackerel \textit{Scomber japonicus} of Pacific subpopulation off central Japan by a daily egg production method. Nippon Suisan Gakkaishi 65: 695-702 (in Japanese with English abstract).

\hangindent=30pt
\noindent
Watanabe, C., Nishida, H. 2002. Development of assessment techniques for pelagic fish stocks: applications of daily egg production method and pelagic trawl in the northwestern Pacific Ocean. Fish. Sci. 68:97-100.

\hangindent=30pt
\noindent
Watanabe, C., Yatsu, A. 2006. Long-tem changes in maturity at age of chub mackerel (\textit{Scomber japonicus}) in relation to population declines in the waters off northeastern Japan. Fish. Res. 78:323-332.

\hangindent=30pt
\noindent
Watanabe, T., 1970. Morphology and ecology of early stages of life in Japanese common mackerel, \textit{Scomber japonicus} HOUTTUYN, with special reference to fluctuation of population. Bull. Tokai Reg. Fish. Res. Lab. 62:1-283 (in Japanese with English abstract).

\hangindent=30pt
\noindent
Williams, B.K., Nichols, J.D., Conroy, M.J. 2002. Analysis and management of animal population. Academic Press, New York.

\hangindent=30pt
\noindent
Yukami, R., Isu, S., Watanabe, C., Kamimura, Y., Furuichi, S. 2019. Stock assessment and evaluation for the Pacific stock of spotted mackerel (fiscal year 2018). In: Marine fisheries stock assessment and evaluation for Japanese waters (2018/ 2019). Fisheries Agency and Fisheries Research Agency of Japan, Yokohama, Kanagawa, p 248−278 (in Japanese).

\hangindent=30pt
\noindent
Yukami, R., Isu. S., Kamimura, Y., Furuichi, S., Watanabe, R., Kanamori, Y. 2020. Stock assessment and evaluation for the Pacific stock of spotted mackerel (fiscal year 2019). In: Marine fisheries stock assessment and evaluation for Japanese waters (2019/ 2020). Fisheries Agency and Fisheries Research Agency of Japan, Yokohama, Kanagawa (in Japanese).

\newpage
\flushleft{\textbf{\Large{Captions}}}\\
\flushleft{\textbf{Fig. 1}} Study area. Spotted mackerel \textit{Scomber australasicus} in the western North Pacific spawns around Kyushu, Shikoku, and the Izu Islands in Japan. Adults and their offspring are then transported to their feeding ground by the Kuroshio Current.
\ \\
\flushleft{\textbf{Fig. 2}} Temporal trends in indices of egg density. The gray line represents the scaled nominal index, the blue line represents the estimated index without the effect of chub mackerel, and the red line represents the estimated index with the effect of chub mackerel. Vertical bars are 95\% confidence intervals of the estimated indices.
\ \\
\flushleft{\textbf{Fig. 3}} Temporal changes in the spatial distribution of relative egg density, \textcolor{red}{as} estimated using the model with the effect of chub mackerel.
\ \\
\flushleft{\textbf{Fig. 4}} Retrospective patterns of total numbers of individuals, total biomass, and spawning stock biomass (SSB). Color differences denote differences in sequentially removing data for the five most recent years (blue, light blue, green, orange, and red indicate removal of data for years 1 to 5 years, respectively) from the full data set (gray).
\ \\

>>>>

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology.
Field surveys using environmental DNA (eDNA) are widely used for detecting invesive or rare species and hotspot of biodiversity (面倒なのでレビュー論文を引用) because the surveys of eDNA are easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al. 2014; Thomsen \& Willerslev 2015 %Dorazioに引用されていたやつ．あとで再確認).
%Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
However, the presence/absence of eDNA includes many types of uncertinties due to relating to environmental factors such as temperature and advection ().
For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.
Therefore, the consideration to the influence of environmental factors on eDNA is necessary for estimation of species distribution when we use eDNA methods.

@@

\ \ \ \ \ \ \ \ \ \ 
Integrated species distribution models are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al. 2020; Miller et al. 2019).

@@

\ \ \ \ \ \ \ \ \ \ 
Tokyo Bay is a large enclosed coastal sea in Japan. In Tokyo Bay, there are many useful species for fisheries that are colled "Edomae" because these species have been used for Sushi since Edo Era (about 400 years ago). Catch of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution). Catch statistics (total catch in each species, efforts, and geographic location of fishing) have been collected for stock assessment since 1990 by prefectures around Tokyo Bay. The strengths of this data are the direct evidence that a focal species occupies a location of fishing and abundant because of widely collected in Tokyo Bay, Japan.  On the other hand, weakness of this data is like a opportunistic data because the data is likely to be biased towards areas to high density of focal species due to commercially fishes, consequently less zero data. In addition to this catch statistics, scientific survey of eDNA has been conducted monthly since 2018 for biodiversity monitoring because biodiversity also may decreased due to human-induced environmental changes (Hongo et al., submitted). The strengths are that the data is systematically collected because of scientific survey data and includes zero data, while the weaknesses are that the data is less abundant and includes uncertinties in presence/absence as description in above.

\ \ \ \ \ \ \ \ \ \ 
%In this paper, we make an integrated spatial distribution model by combining both catch statistics, which is opportunistic data but abundant and represents the direct evidence where fish was, and eDNA data, which is the monitoring data in the same points but not abundant and includes uncertinties due to environmental factors.

%In this paper, we make the model considering with uncertinties caused by environmental factors, such as temperature and advection, to predict spatial distribution of species using an integrated spatial distribution model.

In this paper, to predict spatial distribution of species from eDNA, we first make a model which considers uncertinties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model. We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan. 
The predicted spatial distribution of four fish form our model reduced

@@
